Covariates analysis of MSBB reprocessed RNASeq data

### 2016-06-02 code/Rmd/MSSM_RNASeq_SVA_Reprocessed.Rmd
Added IRW SVA processing pipeline for MSSM reprocessed rnaseq

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq_Reprocessed.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB Reprocessed RNASeq')
```

@@

thisFileName <- 'MSSM_RNASeq_Reprocessed.Rmd'

@@

```{r dataExplore, fig.width = 10, fig.height = 10}
# RIN
p = list()
p[[1]] = ggplot(METADATA, aes(x = as.factor(CDR), y = as.numeric(RIN), fill = as.factor(BrainRegion))) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + theme(legend.position = 'top')

@@

tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`
### Sanity check
```{r residualSigCovars.manual, fig.width=20, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
### Residual calculation
Calculate weighted residuals and add back "BrainRegion.Diagnosis" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("BrainRegion.Diagnosis", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB Reprocessed RNASeq", parentId = parentId)
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq_SVA_Reprocessed.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB Reprocessed RNASeq (with IRW SVA)')
```

@@

thisFileName <- 'MSSM_RNASeq_SVA_Reprocessed.Rmd'

@@

```{r dataExplore, fig.width = 10, fig.height = 10}
# RIN
p = list()
p[[1]] = ggplot(METADATA, aes(x = as.factor(Diagnosis), y = as.numeric(RIN), fill = as.factor(BrainRegion))) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + theme(legend.position = 'top')

@@

tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`
### Sanity check
```{r residualSigCovars.manual, fig.width=20, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
### Estimate surrogate variables using SVA package
```{r sva}
MODEL0 = DM1$design[,-grep('BrainRegion.Diagnosis',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL1 = DM1$design

## Calculate the number of surrogate variables
NUM.SV = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456, LINPACK = TRUE, B = 10)

SURR.VAR = sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0, method = "irw", n.sv = NUM.SV, B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])

DM1$design = cbind(MODEL1, SURR.VAR)

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.FIT,VOOM.ADJUSTED.GENE_EXPRESSION$E)
```

### Residual calculation
Calculate weighted residuals and add back "BrainRegion.Diagnosis" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("BrainRegion.Diagnosis", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB Reprocessed RNASeq (with IRW SVA)", parentId = parentId)
CODE <- synStore(CODE)
